Demographic Groups with Stronger Biden Support in the Election Races

### 2024-03-17 paper/paper.qmd
Final

# Results {#sec-results}
Our results are summarized in @tbl-model-summary-tableLogistic  regression is a common classification algorithm used to predict binary classification problems. In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function. When interpreting the results of logistic regression models. Logistic regression models can provide coefficients (or weights) for each feature variable that represent the relative importance of the feature. The positive and negative symbols of the coefficient can tell us whether the feature has positive or negative influence on the target category, and the absolute value of the coefficient can map the importance of the feature to the target category.

@@

From the @tbl-model-summary-tableLogistic , with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same. The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden. Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
# Discussion {#sec-Discussion}

>>>>

# Results {#sec-results}
Our results are summarized in @tbl-model-summary-tableLogistic, regression is a common classification algorithm used to predict binary classification problems. In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function. When interpreting the results of logistic regression models. Logistic regression models can provide coefficients (or weights) for each feature variable that represent the relative importance of the feature. The positive and negative symbols of the coefficient can tell us whether the feature has positive or negative influence on the target category, and the absolute value of the coefficient can map the importance of the feature to the target category.

@@

From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same. The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden. Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
# Discussion {#sec-Discussion}
